### 2024-02-29 ms.qmd
Updates

We found that the learning slopes for all treatments and species were higher from zero (@tbl-data), but we did not find any difference between treatments or species in the learning rate.  
For _L. delicata_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) (see @fig-deli).

```{r, fig-deli}
#| label: fig-deli
#| fig.cap: "Results for L. delicata. A) Predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean; both obtained by using the slope and intercept estimates from the posterior distributions. The different colours represent the different treatments. B) Distribution of the estimates of the slopes per each treatment. The x-axis represents the estimates of the slopes, and the y-axis represents the density of the estimates. The different colours represent the different treatments."
source(here("R", "func.R"))
# Create the dfs for the probability plot A) (df_prob)
#
df_deliA <- df_fig(as.data.frame(deli), "L. delicata") %>%
  mutate(Trial = gsub("X", "", Trial)) %>%
  mutate(Trial = as.numeric(Trial)) %>%
  group_by(Trial, Treatment, Species) %>%
  summarize(
    Mean_Predicted_prob = mean(Value),
    SE_Predicted_prob = sd(Value)
    ) %>%
  ungroup() %>%
  mutate(
    Treatment = factor(Treatment,
                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
    ) %>%
    select(-Species) %>%
data.frame()
#
# Create the df for the violin plots in plot B) (df_violin)
deliB_list <- list(
  'CORT-Cold' = deli_CORTCold,
  'Control-Cold' = deli_ControlCold,
  'CORT-Hot' = deli_CORTHot,
  'Control-Hot' = deli_ControlHot)
df_deliB1 <- data.frame(
  Value = unlist(deliB_list),
  Treatment = factor(rep(names(deliB_list), each = length(deli_CORTCold)))
)
#
# Create the df for the points and bars in plot B) (df_points)
df_deliB2 <- df_deliB1 %>%
  group_by(Treatment) %>%
  summarize(
    Mean = mean(Value),
    SE = (sd(Value)/sqrt(length(Value))),
    SD = sd(Value)
  ) %>%
  ungroup() %>%
  mutate(
    Treatment = factor(Treatment,
                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot"))
  ) %>%
  data.frame()
# Make plot
fig_deli <- plotting(df_prob = df_deliA, df_violin = df_deliB1, df_points = df_deliB2)
ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 20, height = 10, units = "cm", dpi = 3000)
knitr::include_graphics("./output/figures/fig_deli.png")
```

For _L. guichenoti_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) (@fig-guich).

```{r, fig-guich}
#| label: fig-guich
#| fig.cap: "Results for L. guichenoti. A) Predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean; both obtained by using the slope and intercept estimates from the posterior distributions. The different colours represent the different treatments. B) Distribution of the estimates of the slopes per each treatment. The x-axis represents the estimates of the slopes, and the y-axis represents the density of the estimates. The different colours represent the different treatments."
source(here("R", "func.R"))
# Create the dfs for the probability plot A) (df_prob)
#
df_guichA <- df_fig(as.data.frame(guich), "L. guichenoti") %>%
  mutate(Trial = gsub("X", "", Trial)) %>%
  mutate(Trial = as.numeric(Trial)) %>%
  group_by(Trial, Treatment, Species) %>%
  summarize(
    Mean_Predicted_prob = mean(Value),
    SE_Predicted_prob = sd(Value)
    ) %>%
  ungroup() %>%
  mutate(
    Treatment = factor(Treatment,
                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
    ) %>%
    select(-Species) %>%
data.frame()
#
# Create the df for the violin plots in plot B) (df_violin)
guichB_list <- list(
  'CORT-Cold' = guich_CORTCold,
  'Control-Cold' = guich_ControlCold,
  'CORT-Hot' = guich_CORTHot,
  'Control-Hot' = guich_ControlHot)
df_guichB1 <- data.frame(
  Value = unlist(guichB_list),
  Treatment = factor(rep(names(guichB_list), each = length(guich_CORTCold)))
)
#
# Create the df for the points and bars in plot B) (df_points)
df_guichB2 <- df_guichB1 %>%
  group_by(Treatment) %>%
  summarize(
    Mean = mean(Value),
    SE = (sd(Value)/sqrt(length(Value))),
    SD = sd(Value)
  ) %>%
  ungroup() %>%
  mutate(
    Treatment = factor(Treatment,
                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot"))
  ) %>%
  data.frame()
# Make plot
fig_guich <- plotting(df_prob = df_guichA, df_violin = df_guichB1, df_points = df_guichB2)
ggsave("./output/figures/fig_guich.png", plot=fig_guich, width = 20, height = 10, units = "cm", dpi = 3000)
knitr::include_graphics("./output/figures/fig_guich.png")
```

>>>>

We found that the learning slopes for all treatments and species were higher from zero (@tbl-data), but we did not find any difference between treatments or species in the learning rate.  
For _L. delicata_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`, p-value = `r format_p(pmcmc((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`) (see @fig-deli).

```{r, fig-deli}
#| label: fig-deli
#| fig.cap: "Results for L. delicata. A) Predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean; both obtained by using the slope and intercept estimates from the posterior distributions. The different colours represent the different treatments. B) Distribution of the estimates of the slopes per each treatment. The x-axis represents the estimates of the slopes, and the y-axis represents the density of the estimates. The different colours represent the different treatments. Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
source(here("R", "func.R"))
# Create the dfs for the probability plot A) (df_prob)
#
df_deliA <- df_fig(as.data.frame(deli), "L. delicata") %>%
  mutate(Trial = gsub("X", "", Trial)) %>%
  mutate(Trial = as.numeric(Trial)) %>%
  group_by(Trial, Treatment, Species) %>%
  summarize(
    Mean_Predicted_prob = mean(Value),
    SE_Predicted_prob = sd(Value)
    ) %>%
  ungroup() %>%
  mutate(
    Treatment = factor(Treatment,
                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
    ) %>%
    select(-Species) %>%
data.frame()
#
# Create the df for the violin plots in plot B) (df_violin)
deliB_list <- list(
  'CORT-Cold' = deli_CORTCold,
  'Control-Cold' = deli_ControlCold,
  'CORT-Hot' = deli_CORTHot,
  'Control-Hot' = deli_ControlHot)
df_deliB1 <- data.frame(
  Value = unlist(deliB_list),
  Treatment = factor(rep(names(deliB_list), each = length(deli_CORTCold)))
)
#
# Create the df for the points and bars in plot B) (df_points)
df_deliB2 <- df_deliB1 %>%
  group_by(Treatment) %>%
  summarize(
    Mean = mean(Value),
    SE = (sd(Value)/sqrt(length(Value))),
    SD = sd(Value)
  ) %>%
  ungroup() %>%
  mutate(
    Treatment = factor(Treatment,
                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot"))
  ) %>%
  data.frame()
# Make plot
fig_deli <- plotting(df_prob = df_deliA, df_violin = df_deliB1, df_points = df_deliB2)
ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 20, height = 10, units = "cm", dpi = 3000)
knitr::include_graphics("./output/figures/fig_deli.png")
```

For _L. guichenoti_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`, p-value = `r format_p(pmcmc((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`) (@fig-guich).

```{r, fig-guich}
#| label: fig-guich
#| fig.cap: "Results for L. guichenoti. A) Predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first, and the shaded areas represent the standard deviation of the mean; both obtained by using the slope and intercept estimates from the posterior distributions. The different colours represent the different treatments. B) Distribution of the estimates of the slopes per each treatment. The x-axis represents the estimates of the slopes, and the y-axis represents the density of the estimates. The different colours represent the different treatments. Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
source(here("R", "func.R"))
# Create the dfs for the probability plot A) (df_prob)
#
df_guichA <- df_fig(as.data.frame(guich), "L. guichenoti") %>%
  mutate(Trial = gsub("X", "", Trial)) %>%
  mutate(Trial = as.numeric(Trial)) %>%
  group_by(Trial, Treatment, Species) %>%
  summarize(
    Mean_Predicted_prob = mean(Value),
    SE_Predicted_prob = sd(Value)
    ) %>%
  ungroup() %>%
  mutate(
    Treatment = factor(Treatment,
                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot")),
    ) %>%
    select(-Species) %>%
data.frame()
#
# Create the df for the violin plots in plot B) (df_violin)
guichB_list <- list(
  'CORT-Cold' = guich_CORTCold,
  'Control-Cold' = guich_ControlCold,
  'CORT-Hot' = guich_CORTHot,
  'Control-Hot' = guich_ControlHot)
df_guichB1 <- data.frame(
  Value = unlist(guichB_list),
  Treatment = factor(rep(names(guichB_list), each = length(guich_CORTCold)))
)
#
# Create the df for the points and bars in plot B) (df_points)
df_guichB2 <- df_guichB1 %>%
  group_by(Treatment) %>%
  summarize(
    Mean = mean(Value),
    SE = (sd(Value)/sqrt(length(Value))),
    SD = sd(Value)
  ) %>%
  ungroup() %>%
  mutate(
    Treatment = factor(Treatment,
                        levels = c("CORT-Cold", "Control-Cold", "CORT-Hot", "Control-Hot"))
  ) %>%
  data.frame()
# Make plot
fig_guich <- plotting(df_prob = df_guichA, df_violin = df_guichB1, df_points = df_guichB2)
ggsave("./output/figures/fig_guich.png", plot=fig_guich, width = 20, height = 10, units = "cm", dpi = 3000)
knitr::include_graphics("./output/figures/fig_guich.png")
```
